### 2019-12-05 paper1/paper.tex
Adding Paper 2 (in progress).

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[ICLS/GFM for droplet suspensions under depletion forces] % Short title used in headlines (optional)
{%
  An efficient mass-preserving interface-correction level set/ghost fluid method
  for droplet suspensions under depletion forces% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{An efficient mass-preserving interface-correction level set/ghost fluid method
  for droplet suspensions under depletion forces} % Title for toc
%
\paperauthor[Ge, Loiseau, Tammisola, Brandt] % Short authors used in headlines and List Of Papers
{%
  Zhouyang Ge, Jean-Christophe Loiseau, Outi Tammisola and Luca Brandt%
}%
%
%\listpaperauthor{A. Skywalker \& D. Vader}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden%
}%
%
\paperjournal[J. Comput. Phys.] % Short publish info used in List Of Papers
{%
	Journal of Computational Physics%
}%
%
\papervolume{353}%
%
\papernumber{}%
%
\paperpages{435--459}%
%
\paperyear{2018}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
\todo
}%
%
\graphicspath{{paper1/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

@@

%------------------------------------------------------------------------------
% Abstract
%------------------------------------------------------------------------------
%
\begin{paperabstract}
Aiming for the simulation of colloidal droplets in microfluidic devices, we present here a numerical method for two-fluid systems subject to surface tension and depletion forces among the suspended droplets. The algorithm is based on an efficient solver for the incompressible two-phase Navier-Stokes equations, and uses a mass-conserving level set method to capture the fluid interface. 
The four novel ingredients proposed here are, firstly, an interface-correction level set (ICLS) method; % that efficiently preserves mass. 
global mass conservation is achieved by performing an additional advection near the interface, with a correction velocity obtained by locally solving an algebraic equation, which is easy to implement in both 2D and 3D. 
Secondly, we report a second-order accurate geometric estimation of the curvature at the interface and, 
thirdly, the combination of the ghost fluid method with the fast pressure-correction approach enabling an accurate and fast computation even for large density contrasts. 
Finally, we derive %sharp formulation for the pressure difference 
a hydrodynamic model for the interaction forces
induced by depletion of surfactant micelles and combine it with a multiple level set approach to study short-range interactions among droplets in the presence of attracting forces.
\end{paperabstract}

>>>>

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[ICLS/GFM for droplet suspensions under depletion forces] % Short title used in headlines (optional)
{%
  An efficient mass-preserving interface-correction level set/ghost fluid method
  for droplet suspensions under depletion forces% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{An efficient mass-preserving interface-correction level set/ghost fluid method
  for droplet suspensions under depletion forces} % Title for toc
%
\paperauthor[Ge, Loiseau, Tammisola, Brandt] % Short authors used in headlines and List Of Papers
{%
  Zhouyang Ge, Jean-Christophe Loiseau, Outi Tammisola, Luca Brandt%
}%
%
\listpaperauthor{Z. Ge, J-Ch. Loiseau, O. Tammisola, L. Brandt}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden%
}%
%
\paperjournal[J. Comput. Phys.] % Short publish info used in List Of Papers
{%
	Journal of Computational Physics%
}%
%
\papervolume{353}%
%
\papernumber{}%
%
\paperpages{435--459}%
%
\paperyear{2018}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
\todo
}%
%
\graphicspath{{paper1/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

@@

%------------------------------------------------------------------------------
% Abstract
%------------------------------------------------------------------------------
%
\begin{paperabstract}
Aiming for the simulation of colloidal droplets in microfluidic devices, we present here a numerical method for two-fluid systems subject to surface tension and depletion forces among the suspended droplets. The algorithm is based on an efficient solver for the incompressible two-phase Navier-Stokes equations, and uses a mass-conserving level set method to capture the fluid interface. 
The four novel ingredients proposed here are, firstly, an interface-correction level set (ICLS) method; % that efficiently preserves mass. 
global mass conservation is achieved by performing an additional advection near the interface, with a correction velocity obtained by locally solving an algebraic equation, which is easy to implement in both 2D and 3D. 
Secondly, we report a second-order accurate geometric estimation of the curvature at the interface and, 
thirdly, the combination of the ghost fluid method with the fast pressure-correction approach enabling an accurate and fast computation even for large density contrasts. 
Finally, we derive %sharp formulation for the pressure difference 
a hydrodynamic model for the interaction forces
induced by depletion of surfactant micelles and combine it with a multiple level set approach to study short-range interactions among droplets in the presence of attracting forces.
        \keywords{Multiphase flow, Level set method, Ghost fluid method, Droplet, Depletion force}
\end{paperabstract}
